Figures to insert in text

### 2018-03-14 Chapters/Chapter02.tex
quotes (S. Ulam.)

\begin{flushright}{\slshape
    {Before I came across it, I had read many articles describing intricate properties of neurons, the many varieties of neurotransmitters and second-messenger molecules, synaptic modification processes, complex and hypercomplex cells, columns in the visual cortex, and so on.  All of this was fascinating but seemed very biological and microscopic:  altogether quite distant from everyday mental experiences.  I simply had never come across a cogent theory that addressed brain mechanisms on a global level.  Pentti Kanerva's memory model was a revelation for me: it was the very first piece of research I had ever come across that made me feel I could glimpse the distant goal of understanding how the brain works as a whole. It gave me a concrete sense for how familiar mental phenomena could be thought of as distributed patterns of micro-events, thanks to beautiful mathematics.} \\ \medskip
    --- Douglas Hofstadter}
\end{flushright}
\bigskip
\bigskip

>>>>

\begin{flushright}{\slshape
    {Pentti Kanerva's memory model was a revelation for me: \\
    it was the very first piece of research I had ever come across\\
    that made me feel I could glimpse the distant goal of understanding \\
    how the brain works as a whole. It gave me a concrete sense for\\
    how familiar mental phenomena could be thought of as distributed\\
    patterns of micro-events, thanks to beautiful mathematics.} \\ \medskip
    --- Douglas Hofstadter
    \bigskip
    \bigskip

    {How is memory gradually built up during one's conscious, or\\
    even unconscious, life and thought?  My guess is that everything \\
    we experience is classified and registered on very many parallel \\
    channels in different locations} \\ \medskip
    --- Stanislaw Ulam}
\end{flushright}
\bigskip
\bigskip

### 2018-03-14 Chapters/Chapter03.tex
quotes (S. Ulam.)

As this is a working paper, it is also intended to include the analyses of other datasets, like either Twitter's number of \textit{active users}, or WhatsApp's, or Netflix's, or Reddit's, or Dropbox's, or Waze's. This would enhance the proposed model power of forecasting.

@@

The main limitation of this work is that it has no theory to support which of the models of rejection best fit with empirical data. Although there is an extensive literature on negative word-of-mouth, this literature does not predict which model would be the best. But, if any of these companies discloses the number of \textit{total users} and \textit{active users}, the estimation method could be adapted to estimate the parameters using both pieces of information at the same time, which would make possible to verify which of the models of rejection is the best.

>>>>

As this is a working paper, it is also intended to include the analyses of other datasets, like either Twitter's number of \textit{active users}, or WhatsApp's, or Netflix's, or Reddit's, or Dropbox's, or Waze's, etc. This would enhance the proposed model power of forecasting.

@@

The main limitation of this work is that it has no theory to support which of the models of rejection best fit with empirical data. Although there is an extensive literature on negative word-of-mouth, this literature does not predict which model would be the best. But, if any of these companies discloses the number of \textit{total users} and \textit{active users}, the estimation method could be adapted to estimate the parameters using both pieces of information at the same time, which would make possible to verify which of the models of rejection provides the best fit.

### 2018-03-14 Chapters/Conclusion.tex
quotes (S. Ulam.)

\noindent Modern management and high technology interact in multiple, profound, ways.  Software --- given the widespread availability of general-purpose Turing-complete hardware --- seems to have an immense power of entering arenas which seemed, at some point, to require either specific hardware or the skill of humans.  One of the members of this thesis committee, Dr. Nichols, will participate through teleconferencing over the open web, with no use of hardware specific for the task.  The corporate biography of Tonny Martins, President of IBM Brasil, mentions his successes with blockchain, AI and cognitive technology… as an executive, not as a research scientist or specialized engineer \citep{TonnyMartins}. Professor Andrew Ng tells students at Stanford’s Graduate School of Business that ``AI is the new electricity'' \citep{AndrewNgAI}, as his way to emphasize the potential transformational power of the technology.

>>>>

\noindent Modern management and high technology interact in multiple, profound, ways.  Software --- given the widespread availability of general-purpose Turing-complete hardware --- seems to have an immense power of entering arenas which seemed, at some point, to require either specific hardware or the skill of humans.  One of the members of this thesis committee, Dr. Nichols, will participate through teleconferencing over the open web, with no use of hardware specific for the task.  The corporate biography of Tonny Martins, President of IBM Brasil, mentions his successes with blockchain, AI and cognitive technology… as an executive, not as a research scientist or specialized engineer \citep{TonnyMartins}. Professor Andrew Ng tells students at Stanford’s Graduate School of Business that ``AI is the new electricity'' \citep{AndrewNgAI}, as his hyperbolic way to emphasize the potential transformational power of the technology.
